\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{stmaryrd}
\usepackage[numbers]{natbib}

\pagestyle{plain}
\input{commands}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Scheduling DAG tasks on multicore real-time systems: a supervised learning approach\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Félicien Fiscus-Gay (ID: 23194149)}
\IEEEauthorblockA{\textit{Computer Science} \\
\textit{Auckland University of Technology}\\
Auckland, New Zealand \\
felicien.fgay@gmail.com}
}

\maketitle
\thispagestyle{plain}

\begin{abstract}
Tasks on real-time systems are becoming more and more complex and
those systems are expanding their processing resources and becoming multicore, complexifying
the scheduling of such time-triggered tasks.
To tackle this growth, the Directed Acyclic Graph (DAG) task model has been introduced and
research has been done on designing heuristics
to address the scheduling of DAGs on a multicore platform.
However, very few papers used machine learning for this problem.\\
In this research, the real-time DAG task scheduling literature is reviewed 
and a supervised machine learning model is designed
using a graph convolutional network, and evaluated 
for scheduling a single DAG task with the goal of minimizing its makespan 
using non-preemptive, global fixed-priority scheduling.
The Integer Linear Programming method has been 
used to compute the output labels for the supervised model to learn on
and a non-preemptive, global fixed-priority scheduler simulator 
has been implemented to compute the exact makespan of a DAG task.
The results showed that the supervised model doesn't learn
and that the supervised learning method seems unfit 
for this kind of problem.
The learning issue is mainly due to the computation of 
the output labels, which will be
investigated further in future works.
\end{abstract}

\begin{IEEEkeywords}
real-time system, scheduling, time-triggered tasks, DAG, multicore, machine learning, supervised learning
\end{IEEEkeywords}


\input{intro.tex}
\input{background.tex}
\input{literature.tex}
\input{methodology.tex}
\input{system_design.tex}
\input{evaluation.tex}
\input{limitations.tex}


\section{Conclusions and Future Works}


In this paper, the DAG task scheduling on multicore systems problem
has been addressed, especially looking at the machine learning
techniques used to tackle this problem.
It has been found that very few papers use machine learning
for this kind of problem and no paper has been found using 
supervised learning for the single DAG multicore scheduling problem.
Hence, a supervised learning model has been designed and evaluated.
Unfortunately, the performance results 
showed how the supervised learning method seems unfit for this kind of 
problem, with the main issue being the computation of the output labels.
Reinforcement learning, on the other hand, appears to yield much better results, comparable
to state-of-the-Art heuristics and the optimal Integer Linear Programming method.

Future works should be done on computing unique and more informative output labels,
to expand on the results' discussion,
and, if successful, expand the model to tackle multi-DAGs scheduling as well. 
One could also work on using reinforcement learning for 
multi-rate DAGs, or chain of time-triggered tasks, and potentially
extend the task model to include other types of tasks,
such as Logical Execution Time tasks.










\section*{Acknowledgement}

A special thank you to my supervisor Dr. Matthew Kuo
who guided me throughout this dissertation,
as well as my friend Alexi Cannesse who helped 
me to debug some code when implementing the machine learning model.


\bibliographystyle{IEEEtranN}
\bibliography{references}


\end{document}
